Function to find association b/w n significant eigen genes of meta modules with Diagnosis, Diagnosis.Gender, ApoE

### 2017-10-09 code/Rmd/networkAssociationTest_metaModules.Rmd
Added markdown to perform association test between Dx and aggregated modules

### Store results in synapse
```{r syn.store, include=FALSE, eval = F}
write.table(Dx, file = 'AssociaitonStatWithDx.tsv', sep = '\t', quote = F, row.names = F)
OBJ = File('AssociaitonStatWithDx.tsv', name = 'Association with Dx', parentId = 'syn10831307')
OBJ = synStore(OBJ, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(Dx.gender, file = 'AssociaitonStatWithDxGender.tsv', sep = '\t', quote = F, row.names = F)
OBJ1 = File('AssociaitonStatWithDxGender.tsv', name = 'Association with Dx.Gender', parentId = 'syn10831307')
OBJ1 = synStore(OBJ1, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(Pathway.enrich, file = 'PathwayEnrichment.tsv', sep = '\t', quote = F, row.names = F)
OBJ2 = File('PathwayEnrichment.tsv', name = 'Pathway Enrichment', parentId = 'syn10831307')
OBJ2 = synStore(OBJ2, used = all.used.ids, executed = thisFile, activityName = activityName)

save(list = c('assoc.stat.diagnosis', 'assoc.stat.diagnosis.gender'), file = 'AllAssociationResults.RData')
OBJ3 = File('AllAssociationResults.RData', name = 'All Assocition Statistics (RData)', parentId = 'syn10831307')
OBJ3 = synStore(OBJ3, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(Dx.enrich, file = 'DiagnosisEnrichment.tsv', sep = '\t', quote = F, row.names = F)
OBJ4 = File('DiagnosisEnrichment.tsv', name = 'Diagnosis Enrichment', parentId = 'syn10831307')
OBJ4 = synStore(OBJ4, used = all.used.ids, executed = thisFile, activityName = activityName)
```

>>>>

### Find overlap between modules in different brainregion
```{r module.overlap}

```

### Intereating modules
```{r int.modules}

```

### Store results in synapse
```{r syn.store, include=FALSE, eval = F}
write.table(Dx, file = 'AssociaitonStatWithDx.tsv', sep = '\t', quote = F, row.names = F)
OBJ = File('AssociaitonStatWithDx.tsv', name = 'Association with Dx', parentId = 'syn11140497')
OBJ = synStore(OBJ, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(Dx.gender, file = 'AssociaitonStatWithDxGender.tsv', sep = '\t', quote = F, row.names = F)
OBJ1 = File('AssociaitonStatWithDxGender.tsv', name = 'Association with Dx.Gender', parentId = 'syn11140497')
OBJ1 = synStore(OBJ1, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(Pathway.enrich, file = 'PathwayEnrichment.tsv', sep = '\t', quote = F, row.names = F)
OBJ2 = File('PathwayEnrichment.tsv', name = 'Pathway Enrichment', parentId = 'syn11140497')
OBJ2 = synStore(OBJ2, used = all.used.ids, executed = thisFile, activityName = activityName)

save(list = c('assoc.stat.diagnosis', 'assoc.stat.diagnosis.gender'), file = 'AllAssociationResults.RData')
OBJ3 = File('AllAssociationResults.RData', name = 'All Assocition Statistics (RData)', parentId = 'syn11140497')
OBJ3 = synStore(OBJ3, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(Dx.enrich, file = 'DiagnosisEnrichment.tsv', sep = '\t', quote = F, row.names = F)
OBJ4 = File('DiagnosisEnrichment.tsv', name = 'Diagnosis Enrichment', parentId = 'syn11140497')
OBJ4 = synStore(OBJ4, used = all.used.ids, executed = thisFile, activityName = activityName)
```
